Applying Spatio-temporal Scan Statistics and Spatial Autocorrelation Statistics to identify Covid-19 clusters in the world.

### 2021-01-12 Notebooks/paper_covid.rmd
Update paper_covid.rmd

  In April global cases of Covid-19 reached 1 million, in the same month the world also reached 3 million cases $\!\!^1\!^0$, with an exponential growth in the number of infections, the Global Moran's I was also very high for the number of deaths per inhabitant, while local spatial association was strong only in Europe, the boxmap **(Picture 3)** shows that all areas identified with local dependence for the number of deaths per inhabitant were either HH (High-High) clusters in April or HL (High-Low) clusters after April, which means that generally locations with a high number of deaths were close to other areas that also had a high number of deaths.

@@

[3] - WHO announces COVID-19 outbreak a pandemic. World Health Organization Regional Office for Europe. [S.l.]. Publicado em: 12/03/2020. <https://www.euro.who.int/en/health-topics/health-emergencies/coronavirus-covid-19/news/news/2020/3/who-announces-covid-19-outbreak-a-pandemic>. Acesso em: 24/11/2020.

@@

[10] - Brodeur, *et al*. (2020): A Literature Review of the Economics of COVID-19, GLO Discussion Paper, No. 601, GlobalLabor Organization (GLO), Essen. Available at: http://hdl.handle.net/10419/222316

>>>>

  In April global cases of Covid-19 reached 1 million, in the same month the world also reached 3 million cases $\!\!^3$, with an exponential growth in the number of infections, the Global Moran's I was also very high for the number of deaths per inhabitant, while local spatial association was strong only in Europe, the boxmap **(Picture 3)** shows that all areas identified with local dependence for the number of deaths per inhabitant were either HH (High-High) clusters in April or HL (High-Low) clusters after April, which means that in general locations with a high number of deaths were close to other areas that also had a high number of deaths.

@@

[3] -  Brodeur, *et al*. (2020): A Literature Review of the Economics of COVID-19, GLO Discussion Paper, No. 601, GlobalLabor Organization (GLO), Essen. Available at: http://hdl.handle.net/10419/222316

@@

[10] -
